Boosted

### 2016-04-06 boost_tree.rmd
wrote some stuff to go in the final write up

#partial dependence plots:
i=8
a<- plot.gbm(boost.1, i, type="response")
a
#Discipline, Business, inv.mlsto.log, client.totinv.log, Billing.Type dont matter?

>>>>

#partial dependence plots:
i=1
a<- plot.gbm(boost.1, i, type="response")
a
#Discipline, Business, inv.mlsto.log, client.totinv.log, Billing.Type dont matter?
